### 2015-06-10 ncdnpaper/Response.tex

Reviewer A :

Answer to A-1: Dynamic content (e.g. a dynamically generated web page) is outside the scope of this work. That said,  dynamic content  generates a much smaller volume of traffic compared to static content which includes on-demand video and downloads. An NCDN will see a significant reduction in MLU from caching only the static content.

Answer to A-2: The total storage provisioned at all nodes for a storage ratio of 1 is in the range 228 GB (News Trace) to  895 GB (Downloads Trace). The provisioned storage is likely to be much larger if an NCDN were to cache  content from all content providers. Since it is difficult to estimate the total storage requirement, discussing results in terms of storage ratios is more relevant.

A TE scheme with a lower MLU is better. It enables an ISP to reduce its capital cost by delaying link upgrades. A very high link utilization can adversely affect performance by increasing loss rate and queuing delay.

We plan to improve the presentation of Section 5 as suggested by the reviewer.

Central thesis ??

Reviewer B:

The reviewer correctly observes that LRU caching achieves a high cache hit rate which reduces network traffic significantly. But, this does not explain why InvCap routing achieves nearly the same network cost as an optimized routing.  For the traffic due to cache misses,  optimized routing is expected to achieve a lower network cost compared to InvCap routing. Our results show otherwise.

Our next contribution is to quantify the difference between InvCap+LRU and possibly the ``ideal'' strategy Opt(R+P)Future; we show InvCap+LRU achieves close to the best possible network cost in most cases.

We have performed all our experiments with smaller sized chunks of content  instead of complete content. These experiments do not qualitatively change our findings (Graphs omitted from paper due to lack of space). In fact, we find that chunking of content  helps InvCap+LRU move closer to Opt(R+P)Future.

Reviewer C:

NCDN architecture is more compelling now than it was a few years ago because a greater

The driving factor for an NCDN architecture is the growth of on-demand video (excluding IPTV) on the Internet such as Youtube, Netflix, Hulu. References 5, 15,  in paper show the recent and projected growth of this traffic . Licensed-CDN software for NCDNs from Akamai, EdgeCast, and HP also use the growth in over the top video as the motivating example while marketing their products.

We use the Akamai traces to experiment with a realistic pattern of content requests which a network receives across PoPs over time. To this end, we map each entry in the trace irrespective of the ISP which they originated from to the geographically closest PoP on the current ISP topology we are experimenting with,  Abilene or AT\&T.

We have performed our experiments on the real AT\&T topology as well. We could not include the results in our submission since we did not have formal approval to publish results based on the data. Our results are similar to those on the AT\&T topology from RocketFuel. We expect to have formal approval to use AT\&T topology by the time of the final version of the paper.

### 2015-06-10 auspice_prev/abstract.tex
Initial import of thesis starting from proposal document
Includes all files: tex, pdf, etc.

%!TEX root = Main.tex
\begin{abstract}
Mobile devices dominate the Internet today, however the Internet rooted in its tethered origins continues to provide poor infrastructure support for mobility. Our position is that in order to address this problem,  a key challenge that must be addressed is the design of a massively scalable global name service that rapidly resolves identities to network locations under high mobility. Our primary contribution is the design, implementation, and evaluation of \auspice, a next-generation global name service that addresses this challenge. A key insight underlying \auspice\ is a {\em demand-aware} replica {placement engine} that intelligently replicates name records to provide low lookup latency,  low update cost, and high availability.  We have implemented a prototype of \auspice\ and compared it against several commercial managed DNS providers as well as state-of-the-art research alternatives, and shown that \auspice\ significantly outperforms both. We  demonstrate proof-of-concept that \auspice\ can serve as a complete end-to-end mobility solution as well as enable novel context-based communication primitives that generalize name- or address-based communication in today's Internet.

>>>>

%!TEX root = New.tex
\begin{abstract}

%The Internet's tremendous success as well as our maturing realization of its architectural shortcomings have attracted significant research attention towards clean-slate re-designs in recent times. A number of these shortcomings can be traced back to {\em naming} issues, especially in the manner IP addresses conflate identity and network location, e.g., the poor support for mobility and multihoming; vulnerability to hijacking and spoofing of addresses; the inability of a receiver to control traffic; etc.

Mobile devices dominate the Internet today, however the Internet continues to operate in a manner similar to its early days with poor infrastructure support for mobility. Our position is that in order to address this problem, 
a key challenge that must be addressed is the design of a massively scalable global name resolution infrastructure that rapidly resolves identities to network locations under high mobility. Our primary contribution is the design, implementation, and evaluation of \auspice, a next-generation global name resolution service that addresses this challenge. A key insight underlying \auspice\ is a {placement engine} that replicates name records to provide low lookup latency,  low update cost, and high availability. %\auspice\ employs a heuristic placement algorithm that determines the number and locations of resolver replicas so as to reduce user-perceived response times and update cost while ensuring that no replica location becomes a load hotspot. 
We have implemented a prototype of \auspice\ and compared it against several commercial managed DNS services as well as alternative replication strategies. Further, we present a proof-of-concept validation of end-to-end mobility and novel case-study apps leveraging \auspice's support for context-aware communication that generalize address- or name-based communication.

### 2015-06-10 auspice_prev/appendix.tex
Initial import of thesis starting from proposal document
Includes all files: tex, pdf, etc.

%!TEX root = Main.tex
\appendix

\section{Scalability}
\label{sec:scalability}

\begin{figure}[t]
\centering
\includegraphics[scale=0.6]{graph/newgraphs/scalability.pdf}
\caption{\auspice's consistently gives close to 2$\times$ lower latencies for workloads with 100K-100M names.}
\vspace{-0.2in}
\label{fig:scalability}
\end{figure}

%How will \auspice\ perform at a scale of 10 billion mobile devices? 
To evaluate \auspice's key design traits at very high scales, we evaluate \auspice\ on workloads with 100K-100M device names.  We use a testbed of 200 Amazon EC2 instances, 100 each for nameservers and local nameservers respectively. We emulate wide-area latencies among servers as in the experiments in Section \ref{sec:lookup}. The experiment with a workload of 100M names included 1 billion requests with an equal number of lookups and updates sent over a 4 hour duration. Experiments with lesser number of names proportionally scale down the number of requests and the  duration.  
%As our focus is on evaluating the performance of \auspice's data plane, \auspice\ pre-computes the placement at the start of the experiment based on prior knowledge of the workload. Local name servers are also aware of the precomputed placement and they send requests directly to the active replicas in this experiment. Evaluating  \auspice's control plane performance at larger scales is part of our ongoing work.

Figure \ref{fig:scalability} shows that median lookup latency for Auspice and for \staticthree. We find that \auspice\ consistently gives close to 2$\times$ lower latency than \staticthree\ across all four workloads. 
\auspice's performance is consistent across workloads because its placement strategy ensures a similar distribution of load across name servers independent of the number of names in the workload.
Given that \auspice\ shows similar relative performance across 4 orders of magnitude of variation in the number of names, we expect these properties to persist at higher scales. Intuitively, this result is not surprising: the core of \auspice's replica placement engine is designed to make between M (the minimum required for fault-tolerance) and N (the total number of nameservers) replicas and use all available resources for intelligent replication. Group changes, although nontrivial in design, do not impose a high control overhead.

>>>>

%!TEX root = Main.tex
%\appendix

### 2015-06-10 auspice_prev/bg.tex
Initial import of thesis starting from proposal document
Includes all files: tex, pdf, etc.

%!TEX root = Main.tex
\vspace{-0.1in}
\section{Case for a global name service}
\label{sec:case}

Given the huge body of prior work specifically on mobility as well as more broadly on Internet architecture, it is natural to  begin by asking:  Is a global name resolution service critical to handling mobility if we had the luxury of refactoring Internet naming and routing from a clean slate? %In this section, we first present subjective arguments to justify an affirmative position on this question, and then describe DNS's shortcomings as a resolution service under high mobility for today's Internet.

@@

\newcommand{\indirection}{indirection-based routing}
\newcommand{\Indirection}{Indirection-based routing}
\newcommand{\Logcen}{Global name-to-address resolution}
\newcommand{\logcen}{global name-to-address resolution}
\newcommand{\namerouting}{name-based routing}
\newcommand{\Namerouting}{Name-based routing}

{\textbf \Indirection} schemes are simple as an endpoint remains oblivious to the mobility of other endpoints. No name-to-address\footnote{We use the terms {\em name} and {\em identifier} interchangeably; likewise for the terms {\em address} and {\em location}.} lookup is needed at connection initiation time as a human-readable name maps to a {\em home address} (an IP address in Mobile IP \cite{MIP} or a flat identifier's consistent-hash location in i3 \cite{i3}) that rarely changes by design. Mid-connection mobility, even when both endpoints move concurrently, is seamless to endpoints. However, the data plane pays the price for this simplicity---every data packet must be routed via an indirection agent at the home address, potentially causing significant routing stretch, e.g., two participants at a conference may in each direction need to detour packets halfway across the world despite being in the same  room. %In the case of i3, routing stretch is incurred both at the overlay DHT layer (to reach a rendezvous point) in addition to stretch in the data plane because of mobility, so the authors suggest several alternatives to optimize this stretch  (e.g., choosing the closest of several rendezvous points;  caching IP addresses to handle the conference room scenario, etc.). 
%Mobile IP's sender-oblivious design works well for mobility but is forced to either offer an inflexible design for multihoming or sacrifice sender-obliviousness.  
Furthermore, indirection-based schemes require widespread deployment of indirection agents across different domains, posing a barrier to immediate adoption.

{\textbf \Logcen} schemes rely on a distributed service %that is distinct from the underlying network
to resolve names to addresses as the first step in connection establishment. The current Internet's DNS as well as a number of designs addressing the Internet's so-called identity-location conflation problem also need such a resolution infrastructure, e.g., to translate a self-certifying host identifier in HIP \cite{HIP}, AIP\cite{AIP}, XIA\cite{XIA}, or MobilityFirst\cite{MobilityFirst-UMASS}) or an identifier in LISP \cite{LISP} or HAIR \cite{HAIR} to either an IP address \cite{HIP}, a self-certifying network identifier \cite{AIP,XIA,MobilityFirst-UMASS}, or a hierarchical locator \cite{HAIR} that encodes routing information. \Logcen\ schemes also subsume DHT-based Internet architectures such as LNA \cite{LNA,DOA} %or others \cite{DOA,UIP} 
as well as resolution systems like CoDoNS \cite{codons-paper} that present a DHT-based drop-in replacement for DNS.

@@

{\Logcen} schemes need explicit  support at endpoints to handle mid-connection mobility. There is a general consensus \cite{Migrate,ECCP,TCP-R} that end-to-end connection migration, i.e., bilaterally without relying on an external service,  suffices to migrate connections efficiently when endpoints move one at a time, but an external resolution service is needed to support concurrent mobility. Although the latter is seen as a rare case in most connection migration work, it can be common in disconnection-tolerant, mobile application scenarios, e.g., when a user closes her laptop at home and opens it at a coffee shop to continue watching a movie, by which time the cloud-hosted virtual server may have been migrated for load balancing.

{\textbf \Namerouting} schemes in the ideal have a tantalizing intellectual lure---to seamlessly handle mobility by routing directly over names  with no resolution step---but are marred by several fundamental and practical challenges. First, \namerouting\ approaches can support seamless mobility only if routing update propagation delays are on the order of milliseconds, a daunting challenge given that interdomain routing can take several minutes to converge today. Second, theoretical results on compact routing \cite{compact-routing} suggest discouraging fundamental trade-offs between the size of forwarding tables at routers and path stretch even without any mobility or multihoming, e.g.,  routing over N flat identifiers entails a prohibitive $\Omega(N)$ forwarding table size per router in order to ensure a small constant stretch factor ($\approx$3) compared to shortest-path routing. Simulation-based studies of flat-label routing strategies (e.g., ROFL \cite{ROFL}) reaffirm pessimistic conclusions about its scalability.

Although it may appear that the scalability limitations of name-based routing can be alleviated by adding a hierarchical structure to names \cite{TRIAD, DONA, CCN} (e.g., NDN-style \cite{CCN} names such as  \verb+/umass/phone42/call3/frame7+), frequent mobility still poses a challenge as routers would have to maintain special forwarding entries for ``displaced names'', i.e., names that move from their hierarchically organized namespace (say, from \verb+/umass+ to \verb+/comcast+ in this example) for longest-prefix matching to work correctly. That is, high mobility effectively makes routing directly over structured names as hard as routing over flat names unless indirection or a name resolution infrastructure is used, a conjecture that has recently been empirically reinforced by Gao et al. \cite{Gao14LocInd}.

@@

{\bf{Summary.}} Our position is that a \logcen\ service is critical for handling high mobility in any network architecture as it offers the best combination of trade-offs: (1) a constant update overhead per mobility event to the name service, (2) a modest connection establishment overhead and rapid mid-connection mobility, (3) no data path inflation beyond underlying policy routing, and (4) small forwarding table sizes in conjunction with aggregatable addresses (IP prefixes like today or self-certifying network addresses \cite{MobilityFirst-UMASS,XIA}). Perhaps the most compelling argument for  \logcen\ is our decades of familiarity with DNS and the Internet; handling mobility would be a drop-in replacement to DNS provided we address the challenge of building a distributed system that scales to billions of devices making many updates a day and yet returns up-to-date responses within milliseconds. %Addressing this challenge is the focus of the rest of this paper.

\subsection{Limitations of DNS}
\label{sec:whyNotDNS}

\blue{
What specific design traits of DNS make it poorly suited for mobile applications? The first two traits below limit its scalability with respect to the rate of endpoint mobility, and the third limits its scalability with respect to the size of the namespace if applications were to have the luxury of using arbitrary (but fixed) names.
}

\blue{ 
(1) {\em TTL-based caching:} TTL-based caching is the single-most important mechanism for DNS's scalability; caching not only helps DNS sustain essentially arbitrarily high {\em lookup load} but also dramatically reduces client-perceived {\em lookup  latency} for cache hits. However, caching is ineffective when TTLs are near-zero, as would have to be the case under high mobility, causing both increased load on name servers and higher client-perceived latencies. Caching is also less effective if lookups are distributed relatively uniformly, as could be the case with mobile device names, unlike lookups for today's domain names that are highly skewed \cite{Jung, DHTdns}.
}

\blue {
(2) {\em Static placement:} Authoritative DNS servers are essentially rendezvous points that allow a mobile endpoint to inform potential correspondents of its current location(s). In order to reduce the time-to-connect, authoritative servers must be located close to potential correspondents. However, authoritative server locations today are static, either close to a mobile endpoint's ``home'' location or a pre-packaged set of geo-distributed locations provided by a managed DNS provider. Engineering a scalable geo-distributed system that can dynamically move object replicas in a demand-aware manner is nontrivial and real-world examples of such systems have only recently begun to emerge \cite{spanner}.
}

%\blue{
(3) {\em Hierarchical names:} The hierarchical structure of DNS names is key to leveraging {\em federation} to scale to an arbitrary {number of names} by delegating different portions of the name space (or {zones}) to different organizations. For example, root name servers today only have to maintain state for a small number of top-level domain names.  In contrast, arbitrary or flat names, e.g., ``\verb+JohnSmith3142's watch+'' can not be supported in DNS while retaining the scaling benefits of federation as the root name servers would have to maintain nonzero state, e.g., at least the authoritative name server(s) and the DNSSEC key of a name, for essentially all names. Our position is that the design of a general-purpose global name service must not restrict the structure of names as names carry application-specific semantics; in $\S$\ref{sec:context}, we show examples of novel context-aware communication primitives that are feasible with unrestricted names.
%}

\blue{
{{Our approach}} to address the first two issues above relies on {\em active} and {\em demand-aware} replication: (1) Active replication significantly reduces (but does not eliminate) the reliance on passive caching; (2) Demand-aware replication ensures that active replicas of a name record are accessible close to clients querying the name, so as to reduce the overall {time-to-connect}. A glib but pedagogically helpful way to highlight the difference from DNS is that, in the extreme case, our approach can create an active replica of a name record near every DNS local name server that stores a passively cached copy today. Our approach addresses the third issue above by cleanly separating resolution of names from adjudication and certification. We explain our approach in detail next.
}

>>>>

%!TEX root = Main.tex
\vspace{-0.1in}
\section{Global name resolution: Why care?}

Given the huge body of prior work specifically on mobility as well as broader efforts on Internet architecture, it is natural to ask:  is a global name resolution service critical to handling mobility if we had the luxury of re-architecting Internet naming and routing from a clean slate? %In this section, we first present subjective arguments to justify an affirmative position on this question, and then describe DNS's shortcomings as a resolution service under high mobility for today's Internet.

@@

}
{\textbf \Indirection} schemes are simple as an endpoint remains oblivious to the mobility of other endpoints. No name-to-address\footnote{We use the terms {\em name} and {\em identifier} interchangeably; likewise for the terms {\em address} and {\em location}.} lookup is needed at connection initiation time as a human-readable name maps to a {\em home address} (an IP address in Mobile IP \cite{MIP} or a flat identifier's consistent-hash location in i3 \cite{i3}) that rarely changes by design. Mid-connection mobility, even when both endpoints move concurrently, is seamless to endpoints. However, the data plane pays the price for this simplicity---every data packet must be routed via an indirection agent at the home address, potentially causing significant routing stretch, e.g., two participants at a conference may in each direction need to detour packets halfway across the world despite being in the same  room. %In the case of i3, routing stretch is incurred both at the overlay DHT layer (to reach a rendezvous point) in addition to stretch in the data plane because of mobility, so the authors suggest several alternatives to optimize this stretch  (e.g., choosing the closest of several rendezvous points;  caching IP addresses to handle the conference room scenario, etc.). 
%Mobile IP's sender-oblivious design works well for mobility but is forced to either offer an inflexible design for multihoming or sacrifice sender-obliviousness.  
Furthermore, indirection-based schemes require widespread deployment of indirection agents across different domains, posing a barrier to immediate adoption.

{\textbf \Logcen} schemes rely on a distributed service %that is distinct from the underlying network
to resolve names to addresses as the first step in connection establishment. The current Internet's DNS as well as a number of designs addressing the Internet's so-called identity-location conflation problem also need such a resolution infrastructure, e.g., to translate a self-certifying host identifier in HIP \cite{HIP}, AIP\cite{AIP}, XIA\cite{XIA}, or MobilityFirst\cite{MobilityFirst-UMASS}) or an identifier in LISP \cite{LISP} or HAIR \cite{HAIR} to either an IP address \cite{HIP}, a self-certifying network identifier \cite{AIP,XIA,MobilityFirst-UMASS}, or a hierarchical locator \cite{HAIR} that encodes routing information. \Logcen\ schemes also subsume DHT-based Internet architectures such as LNA \cite{LNA} or others \cite{DOA,UIP} as well as resolution systems like CoDoNS \cite{codons-paper} that present a DHT-based drop-in replacement for DNS.

@@

{\Logcen} schemes need explicit  support at endpoints to handle mid-connection mobility. There is a general consensus \cite{Migrate,ECCP,TCP-R} that end-to-end connection migration, i.e., bilaterally without relying on an external service, can efficiently migrate connections when endpoints move one at a time; however, an external resolution service is needed to support concurrent mobility. Although the latter is seen as a rare case in most connection migration work, it can be a common event for disconnection-tolerant, mobile application scenarios (e.g., when a user closes her laptop at home and opens it at a coffee shop to continue watching a movie, by which time the cloud-hosted virtual server may have been migrated for load balancing).

{\textbf \Namerouting} schemes in the ideal have a tantalizing intellectual lure---to seamlessly handle mobility by routing directly over names obviating a name-to-address resolution infrastructure---but are marred by several fundamental and practical challenges. First, \namerouting\ approaches can support seamless mobility only if route update propagation delays across the Internet are on the order of milliseconds, a daunting challenge given that interdomain routing can take several minutes to converge today. Second, theoretical results on compact routing \cite{compact-routing} suggest discouraging fundamental trade-offs between the size of forwarding tables at routers and path stretch even without any mobility or multihoming, e.g.,  routing over N flat identifiers entails a prohibitive $\Omega(N)$ forwarding table size per router in order to ensure a small constant stretch factor ($\approx$3) compared to shortest-path routing. Simulation-based studies of flat-label routing strategies (e.g., ROFL \cite{ROFL}) reaffirm pessimistic conclusions about its scalability. Although it may appear that the scalability limitations of name-based routing can be alleviated by adding a hierarchical structure to names \cite{TRIAD, DONA, CCN} (e.g., NDN \cite{CCN} names such as  \verb+/parc/jsmith_phone/voip_call3/frame7+), frequent mobility still poses a challenge as routers would have to maintain special forwarding entries for ``displaced names'' when the name moves from its hierarchically organized namespace for longest-prefix matching to work correctly, i.e., high mobility effectively makes routing directly over structured names as hard as routing over flat names unless indirection or a name resolution infrastructure is used.

@@

In {summary}, our position is that a \logcen\ service is critical to handling high mobility in any network architecture as it offers the best combination of trade-offs: (1) a constant update overhead per mobility event to the name service, (2) a modest connection establishment overhead and rapid mid-connection mobility, (3) no data path inflation beyond underlying policy routing, and (4) small forwarding table sizes in conjunction with aggregatable addresses (IP prefixes like today or self-certifying network addresses \cite{MobilityFirst-UMASS,XIA}). Perhaps the most compelling argument for the \logcen\ approach is our decades of familiarity with DNS and the current Internet; handling mobility would be a drop-in replacement to DNS provided we can address the challenge of building a distributed system that can scale to billions of devices making tens of updates a day and yet return responses within a few milliseconds. %Addressing this challenge forms the focus of the rest of the paper.

%In {summary}, we posit that all mobility approaches must either rely on a logically centralized resolution service in order to scale, or adopt an indirection-based approach and inherit their drawbacks. A logically centralized approach offers the best combination of traits: (i) a small update overhead per mobility event to the name service, (ii) efficient mid-session mobility, (iii) no data path inflation beyond underlying policy routing, and (iv) small forwarding table sizes in conjunction with aggregatable network addresses (IP prefixes like today or self-certifying network addresses \cite{MobilityFirst,XIA}). Perhaps the most compelling argument for the logically-centralized approach is our decades of familiarity with DNS and the current Internet; handling mobility would be a drop-in replacement to DNS provided we can address the challenge of building a distributed system that can scale to billions of devices making tens of updates a day and yet return responses within a few milliseconds. Addressing this challenge forms the focus of the rest of the paper.
